%-------------------------
% Resume in Latex
% Author : Emma Lewis
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.0in}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Emma Lewis}} & Email : \href{mailto:eelewis@uw.edu}{eelewis@uw.edu}\\
  \href{}{} & Mobile : \href{tel:+13609890832}{+1-360-989-0832} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California Santa Barbara}{Santa Barbara, CA}
      {Bachelor of Arts in Environmental Studies;  GPA: 3.8}{Sep. 2019 -- 2022}
        \resumeItemListStart
            \resumeItem{Relevant Coursework}
            {Environmental Economics, Environmental Law, Ocean Policy, Organic Chemistry}
        \resumeItemListEnd
    \resumeSubheading
    {University of Washington}{Seattle, WA}
    {Bachelor of Science in Oceanography;  GPA: 3.6}{Sep. 2022 -- Current}
    \resumeItemListStart
        \resumeItem{Relevant Coursework}
        {Marine Biology, Marine Geology, Marine Chemistry, Marine Ecology}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Assistant in Environmental Studies Department, UCSB}{Santa Barbara, CA}
      {Research Assistant}{Jan 2021 - Aug 2022}
      \resumeItemListStart
        \resumeItem{Plastic Pollution Study}
          {Participated in a research project studying the impact of plastic pollution on marine ecosystems. Collected and analyzed samples, prepared reports, and contributed to the publication of our findings in a leading environmental science journal.}
        \resumeItem{Community Outreach}
          {Organized and led community outreach programs to educate the public about environmental issues and sustainable practices.}
        \resumeItem{Environmental Impact Assessment}
            {Assisted in conducting an environmental impact assessment for a proposed construction project. Our report influenced the decision to implement additional mitigation measures to protect local wildlife.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Researcher in Oceanography Department, UW}{Seattle, WA}
      {Student Researcher}{Sep 2022 - Present}
      \resumeItemListStart
        \resumeItem{Ocean Acidification Study}
          {Currently leading a study investigating the effects of ocean acidification on shellfish populations in the Puget Sound.}
        \resumeItem{Data Analysis}
          {Regularly perform data analysis using tools such as Python and R to interpret and visualize data collected during our research.}
        \resumeItem{Fieldwork}
            {Conduct regular fieldwork to collect samples and monitor local marine ecosystems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Estuary Restoration Project (GIS / Ecology)}
      {Conducted a comprehensive ecological assessment for a local estuary restoration project. Used GIS tools to map the area and identify key restoration targets. Presented findings to local stakeholders and helped secure funding for the project.}
    \resumeSubItem{Climate Change Impact Assessment (Climate Modeling /```latex
Data Analysis)}
      {Completed a climate change impact assessment for the Santa Barbara region. Used climate models to predict future temperature and precipitation patterns. Results were used to inform local climate change mitigation strategies.}
    \resumeSubItem{Microplastics in Marine Food Chain (Marine Biology / Chemistry)}
      {Investigated the presence and effects of microplastics in the marine food chain. Conducted laboratory tests to determine plastic content in various fish species.}
    \resumeSubItem{Coral Reef Health Monitoring (Marine Biology / Data Analysis)}
      {Developed a monitoring system for coral reef health in a popular snorkeling area. Used underwater photography and image analysis techniques to assess coral health and diversity over time.}
    \resumeSubItem{Ocean Acidification Monitoring (Oceanography / Data Analysis)}
      {Set up an ocean acidification monitoring station in Puget Sound. Collect and analyze data on a regular basis to track changes in water chemistry.}
    \resumeSubItem{Sustainable Campus Initiative (Sustainability / Community Outreach)}
      {Led a student initiative to reduce waste and increase recycling on the UCSB campus. Organized events, coordinated with campus administration, and successfully implemented several key initiatives.}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Field Work Skills}{: Water Quality Testing, Soil Sampling, Ecological Surveying, GPS Navigation}
      \hfill
      \textbf{Laboratory Skills}{: Microscopy, Spectrophotometry, Water & Soil Analysis}
      \hfill
      \textbf{Software Skills}{: ArcGIS, QGIS, MATLAB, R (tidyverse, ggplot2), Python (numpy, pandas, matplotlib)}
      \hfill
    }
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}